Draft

### 2020-08-09 Draft.Rmd
Final submitted version of draft

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE)
```

@@

With correct model specification being an ongoing issue for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of this misspecification. Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
Results at the current stage have shown that the greater the degree of model misspecification is, the more beneficial is optimal prediction. Empirical analysis shows that after the global financial crisis, predictions that are optimal according to a censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate than the alternatives, including likelihood-based predictions. This indicates the potentially significant contribution to financial analyses of this method.

@@

@@

This research paper will explore the question: ‘When do optimal probabilistic forecasts work’; with particular attention given to the usefulness of optimal predictions in financial markets. This work builds on recent research on this topic by Loaiza-Maya et al. (2020). Probabilistic forecasts can provide complete information about future uncertainty, which could be more valuable than point and interval forecasts to forecasters. However, both Bayesian and frequentist prediction assume that the underlying model correctly specifies the process that has generated the observations. While in practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generation process (DGP). This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.

As an alternative to likelihood-based prediction, scoring rules have been introduced before to produce and evaluate probabilistic forecasts. A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity (Gneiting & Raftery, 2007). Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al. (2020) and Opschoor, van Dijk & van der Wel (2017). Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by Diks, Panchenko & van Dijk (2011), captures our attention since its ‘focusing’ feature shows great values in financial risk management. In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.

The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al. (2020). It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule. However, the discussion of whether the optimal forecasts’ performance differs among different types of model misspecification is left to blank, and the financial application of optimal forecasts can be further investigated among different financial instruments.

This research paper extends the work of Loaiza-Maya et al. (2020) to investigate the effects of the form and degree of model misspecification on optimal forecast performance and to conduct empirical analysis on how optimal forecasts perform in Value-at-Risk (VaR), the Volatility Index (VIX) and portfolio optimization applications, using empirical data extending over a period of time that precedes the global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacted on financial markets.

Section 2 documents how scoring rules work in producing and evaluating the optimal forecasts under both simulation and empirical settings. The background and notation of scoring rules used in this paper are provided at the start. Besides, the simulation analysis investigates the effects of different forms and degrees of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models. The assumed predictive model is fixed as ARCH (1) for the purpose of manipulating the degree of model misspecification. The performance of optimal forecasts in practice is also shown in this section, conducted with S&P500 daily log return data. In section 3, we look at the financial application of scoring rules in VaR using both simulated and S&P500 observations with same methodology adopted in section 2. The analysis of VIX is provided in section 4, and the predictive model is HAR-RV model with different error term specifications. We conclude and discuss any possible caveats in section 5.

# 2. Scoring rule in prediction
## 2.1 Overview and notation

Scoring rules can be used in both estimation and prediction. In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$ on the condition that $S_n$ is positively oriented. That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$, $\hat \theta \to \theta$ as $n \to \infty$. While in prediction, scoring rules assign a numerical value to density forecasts, simultaneously addressing both sharpness and calibration (Gneiting & Reftery, 2007). For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates. The crucial importance of the propreity of scoring rules must be emphasized for the purpose of ranking and comparing forecasts based on scoring rules. Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast and consequently, mess up the prediction evaluation. Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).

Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL focuses on predicting a certain region(s) of densities.

The logarithmic score is defined as (1) where $p_t$ is the probabilistic density forecast. It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007). 
\begin{align}
S_{LS}(p_t, y_{t+1}) = log[p_t(y_{t+1})]
\end{align}
However, logarithmic score is criticized by its unboundness and its local property. Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". Gneiting & Raftery (2007) also argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events. 
\begin{align}
CRPS(P,x)=-\int_{-\infty}^{\infty}(P(y)-I(y\geq x))^2dy
\end{align}
The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
\begin{align}
CRPS(N,x)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x-\mu}{\sigma})-\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
where $\phi$ and $\Phi$ are the probability density function and cumulative density function of the Gaussian predictive distribution.

CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented form as shown in (4) for convenient comparison among scoring rules in following sections. 
\begin{align}
CRPS^*(N,x)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x-\mu}{\sigma})+\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
Both LS and CRPS are used for producing and evaluating the entire predictive density. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose a new proper scoring rule, censored likelihood score, which allows users to assess the forecasts only in the interested region(s) instead of using weights to emphasize a particular part of the entire density forecast. It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
\begin{align}
S_{CSL}(p_t, y_{t+1})=I(y_{t+1} \in A_t)log[ p_t(y_{t+1})]+I(y_{t+1} \in A_t^c)log[\int_{A_t^c} p_t(s)ds]
\end{align}
Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on LS and CRPS.

## 2.2 Numerical investigation
### 2.2.1 Simulation design

Loaiza-Maya, Martin & Frazier (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score. In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which is using logarithmic score for updating the prior probability and they also point out the model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.

Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample. Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance. Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence is when the optimal prediction is strictly preferable given that score. Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1, S_2$, then the prediction is said to be coherent if 
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
\end{align}
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
\end{align}
It is said to be strictly coherent if the equality doesn't hold in (6)(7).

Building on the previous research in this field, we conduct a numerical analysis first in this sub section to further investigate the effects of the form and degree of model misspecification on optimal forecast performance. In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimics the behavior of financial returns and volatility. Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock return's distribution, and the negative marginal skewness will be incorporated by an inversion copula with degree of skewness controlled by the shape parameter. In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.

Specific simulation scenarios are listed in following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

@@

\textbf{Assumed Model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
\end{tabular}
\end{table}

The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively. The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted here. We conduct each simulation scenario as follows:

@@

  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively-oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$

\begin{align}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{align}
\begin{align}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{align}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (10)(11)(12):

\begin{align}
S_{LS}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{align}
\begin{align}
S_{CRPS}^*(P_{\boldsymbol\theta^{t-1}},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{align}
\begin{align}
S_{FSR}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{align}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{align}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{align}

### 2.2.2 Simulation results
#### 2.2.2.1 Average score tables

The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation. The bolded value(s) is the maximum(s) of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column. We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.

@@

The results from Table 1-3 show one particular type of model misspecification. That is, the underlying model ARCH(1) cannot capture the volatility clustering feature of the true data generation process (DGP), thus misspecification. Besides, with the degree of freedom increases, the data generated from GARCH(1,1) model is more like data that are from ARCH(1) and therefore, the degree of model misspecification decreases. When degree of freedom is large enough, we consider ARCH(1) as a correct specified model as shown in Table 1.

From Table 3. we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case. These results are consistent with conclusions from Loiaza-Maya et al.(2020). It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions. That is, we are expected to gain more from optimal forecasts while the degree of model misspecification is high.

Table 4-6 show another type of model misspecification where the underlying model cannot capture the asymmetric feature of the true DGP. The results give similar conclusions to Table 1-3. It proves that optimal forecasts perform in the same way even when we have different types of model mispecification.

#### 2.2.2.2 Score traces plots

As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails. Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2. In the left panel, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

```{r}
# need to adjust the size. 
knitr::include_graphics("figure 1.pdf")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE)

# devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
                    #  filename = 'render_toc.R')
```

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
Results at the current stage have shown that the greater the degree of model misspecification, the more beneficial is optimal prediction. Empirical analysis shows that after the global financial crisis, predictions that are optimal according to the censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions. This indicates the potentially significant contribution to financial analyses of this approach.

@@

```{r toc, echo=FALSE} 
# render_toc("Draft.Rmd")
```

@@

This research paper will explore the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.

Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters. However, previous approaches to prediction - including probabilistic methods - typically assume that the predictive model correctly specifies the process that has generated the observations. In practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generating process (DGP). This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.

As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts. A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007). Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020). Among all these investigations, it is the censored likelihood score (CLS) or the focused score (FSR) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management. In other words, CLS/FSR allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.

The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al. (2020). It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule. Whilst some empirical investigations were undertaken, these were primarily illustrative, with there being much scope left for exploring the performance of optimal methods in forecasting different types of financial measures, and under different assumed models.

This research paper extends the work of Loaiza-Maya et al. (2020) by investigating the effect of the form and degree of model misspecification on optimal forecast performance in particular financial settings; in particular by conducting an empirical analysis of how optimal forecasts perform in Value-at-Risk (VaR), Volatility Index (VIX) and portfolio optimization applications. Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.

The paper proceeds as follows. Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules. Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models. The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification. Although the simulation design is introduced in this section, it forms the foundation of methodologies used in all experiments conducted in other sections of this paper. In Section 4, we emulate the simulation exercise on an empirical example for financial returns of the S&P 500 index, including the prediction of the Value-at-Risk (VaR). The results illustrate the practical contributions to financial risk management. The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications. We conclude and discuss any possible caveats in Section 6.

# 2. Scoring rules in prediction
## 2.1 Overview and notation

Scoring rules are a type of criterion function that can be used in producing and evaluating probabilistic predictions. The crucial importance of the propriety of scoring rules must be emphasized for the usage of scoring rules. Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).

An optimal estimator $\hat \theta_n$ can be obtained by maximizing a scoring rule $S_n(\theta)$ on the condition that $S_n$ is positively oriented. 
\begin{align}
\hat \theta_n=arg \max_\theta S_n(\theta)
\end{align}
Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$. This idea is adopted in both Bayesian and frequentist predictions, where scoring rules replace the role conventionally played by the likelihood function in producing probabilistic forecasts; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020).

In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously (Gneiting & Reftery, 2007). It is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules. For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates. The idea of optimal probabilistic forecasts is that the forecasts produced from a model that is 'optimized' based on a user-specified proper scoring rule will perform the best out-of-sample - according to that same score (Loaiza-Maya et al.,2020). The propriety of scoring rules used in optimal forecasts is important, since improper scoring rules will assign a higher average score to an incorrect density forecast
(Gneiting & Raftery, 2007). Consequently, forecasts based on improper scoring rules will not be 'optimal'.

## 2.2 Some commonly used scoring rules 
A variety of scoring rules have been developed to tackle different problems. Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).

The logarithmic score is defined as (2) where $p_t$ is the predictive density. 
\begin{align}
S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
\end{align}
It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007). Estimators based on the logarithmic score are equivalent to the maximum likelihood estimator (MLE) so that it is included as a benchmark in the following investigations of optimal forecasts' performance.

However, the logarithmic score is criticized for its unboundedness and its local property. Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (3) 
\begin{align}
CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
\end{align}
where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.

The formula can be simplified to (4) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
\begin{align}
CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
\end{align}
where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.

CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in (5) for convenient comparison among scoring rules in the following sections. 
\begin{align}
CRPS^*(N_{t-1},x_t)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x_t-\mu}{\sigma})+\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
\end{align}
Both LS and CRPS are used for producing and evaluating the entire predictive densities. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in (6) 
\begin{align}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{align}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

# 3. Numerical investigation of optimal predictions: simulated data 
## 3.1 Simulation design

Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation. Loaiza-Maya, Martin & Frazier (2019) propose a new method, focused Bayesian prediction (FBP), which replaces the conventional likelihood function with the censored likelihood score. In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which uses the logarithmic score for updating the prior probability and they also point out that model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.

Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample. Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance. Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence happens when the optimal prediction is strictly preferable given that score. Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1$ and $S_2$. The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if 
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
\end{align}
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
\end{align}
It is said to be strictly coherent if (7) and (8) are strict inequalities.

Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts. In order to set the scene for the financial application analysis in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility. Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using an inversion copula model, with the degree of marginal skewness controlled by the shape parameter. In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).

Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

@@

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
\end{tabular}
\end{table}

MLE is a frequently used estimation method in frequentist prediction. It often works with the log-likelihood, which corresponds to the logarithmic scoring rule. Therefore, we use the predictions produced by MLE (LS) as the benchmark of the following comparisons. Besdies, the tails of a density are important for risk management in finance so that we decide to apply the focused scoring rule to the 10%, 20%, 80% and 90% tails of the distribution, corresponding to the risks of long and short portfolios. Certain aspects of the methodology used in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) are adopted here. We conduct each simulation scenario as follows:

Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead prediction based on the assumed model, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ ($P(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$) be the predictive probabilistic (cumulative probabilistic) distribution at time t.

@@

  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$

\begin{align}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{align}
\begin{align}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{align}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):

\begin{align}
S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{align}
\begin{align}
S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{align}
\begin{align}
S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{align}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{align}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{align}

## 3.2 Simulation results
### 3.2.1 Average out-of-sample scores

The first column of each of the following tables presents the labels for the $S_i$ that we used to produce predictions and the third-row shows $S_j$, which is used for the forecast's evaluation. The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column. We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.

@@

The results from Table 1-3 show one particular type of model misspecification. That is, the assumed predictive model, ARCH(1), cannot capture the long term volatility clustering feature of the data generated from GARCH(1,1) models, i.e. the true DGP. Hence, there is misspecification. When the degrees of freedom parameter in the error term of GARCH(1,1) is large enough, the ARCH(1) model is correctly specified as shown in Table 1. As the degrees of freedom decreases, the degree of model misspecification increases.

From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high. These results are consistent with conclusions from Loiaza-Maya et al. (2020). It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions. That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.

Table 4-6 show another type of model misspecification where 
the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP). From Table 4-6, as the shape parameter decreases, the degree of negative marginal skewness increases, and thus the degrees of model misspecification increases. The results give similar conclusions to Table 1-3. It proves that optimal forecasts perform in the same way even when we have different types of model misspecification.

### 3.2.2 Trace plots

The predictive accuracy of tails is important for financial risk management. Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails. The results in Section 3.2.1 shows that when the degree of model misspecification is high, FSR can perform the best compared with MLE and CRPS in predicting tails. However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.

In the left panel of each trace plot, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From Figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

```{r}
# need to adjust the size. 
knitr::include_graphics("figure1.pdf")
```
